---
title: "Project title"
subtitle: "Proposal"
format: html
editor: visual
---

```{r}
#| label: load-pkgs
#| message: false

library(tidyverse)
library(skimr)
library(dplyr)
```

# Data 1

## Introduction and data

-   Identify the source of the data.

    Kaggle: Spotify Tracks Dataset

    Source: <https://www.kaggle.com/datasets/maharshipandya/-spotify-tracks-dataset?resource=download>

-   State when and how it was originally collected (by the original data curator, not necessarily how you found the data).

    The data was collected and cleansed using Spotify's web API and Python by the original data curator.

-   Write a brief description of the observations.

    Each observation is a song. Each row contains the id, artist, album name, song name, popularity, duration, explicitness, rating of danceability, and rating of energy of the song on Spotify.

## Research question

-   A well formulated research question. (You may include more than one research question if you want to receive feedback on different ideas for your project. However, one per data set is required.)

    -   Are the most popular songs on Spotify more danceable? 

    -   Are the most popular songs on Spotify longer in duration?

    -   What genre are the most popular songs on Spotify?

-   A description of the research topic along with a concise statement of your hypotheses on this topic.

    Music is an integral enterprise to our daily life. Whether it be listening to the radio or attending a concert, we experience different types of music at frequent rates. Thus, it's interesting to explore what makes different songs popular; we are especially interested in danceability, duration, and genre. Currently, we hypothesize that the most popular songs on Spotify are highly danceable, short, pop songs.

-   Identify the types of variables in your research question. Categorical? Quantitative?

    -   **Track_id:** Qualitative - description

    -   **Artists:** Qualitative- descriptive

    -   **Duration:** Quantitative

    -   **Album_name:** Qualitative - descriptive

    -   **Track_name:** Qualitative- descriptive

    -   **Popularity:** Quantitative

    -   **Danceability:** Quantitative

    -   **Track_genre:** Categorical

## Glimpse of data

```{r}
#| label: load-spotify-dataset

spotify <- read.csv("data/dataset.csv")

glimpse(spotify)

```

# Data 2

## Introduction and data

-   Identify the source of the data.

    -   Kaggle: "TV shows on Netflix, Prime Video, Hulu, and Disney+"

    -   <https://www.kaggle.com/datasets/ruchi798/tv-shows-on-netflix-prime-video-hulu-and-disney>

-   State when and how it was originally collected (by the original data curator, not necessarily how you found the data).

    -   The data was collected and uploaded in 2021. The curator scraped the available television shows during that time from Netflix, Prime Video, Hulu, and Disney+ and uploaded them to this data set.

-   Write a brief description of the observations.

    -   We have 12 columns and 5368 observations. The columns are the titles of the show (string), whether the show is streamed on Hulu, Disney+, Prime Video, or Netflix, the ranking of the show (integer out of 100), the year it was produced, the target age group (string). We have 1 if the show is streamed on a specific platform, and 0 otherwise. All the shows have a unique identifier.

## Research question

-   A well formulated research question. (You may include more than one research question if you want to receive feedback on different ideas for your project. However, one per data set is required.)
    -   What platform presents the best-quality television shows for each age-group?
-   A description of the research topic along with a concise statement of your hypotheses on this topic.
    -   As streaming platforms continue to grow in popularity, discourse about which platform is best seems to be taking place at an increasingly frequent rate. As such, we\'re interested in learning about platforms\' television offerings per age group (especially ours!). In order to address this interest, we\'re intending on looking at the IMDb and/or Rotten Tomatoes scores (indicating TV quality), age group, and platform for each TV show; we can analyze the research question with these particular variables. Currently, we hypothesize that Netflix will have the highest-quality TV shows for most age groups.
-   Identify the types of variables in your research question. Categorical? Quantitative?
    -   **Row ID:** Quantitative 

    -   **Unique TV ID:** Quantitative

    -   **Title:** Qualitative - Descriptive

    -   **Year:** Quantitative

    -   **Age:** Categorical 

    -   **IMDb Rating**: Quantitative

    -   **Rotten Tomatoes Rating:** Quantitative

    -   **Netflix:** Categorical

    -   **Hulu:** Categorical

    -   **Prime Video:** Categorical

    -   **Disney+:** Categorical

    -   **Type:** Categorical 

    -   NOTE: Some of these variables might be filtered out/manipulated in our cleaned data set; the above list represents the variables in their original form.

## Glimpse of data

```{r}
#| label: load-tvshows-dataset

tvshows <- read.csv("data/tv_shows.csv")

glimpse(tvshows)

```

# Data 3

## Introduction and data

-   Identify the source of the data.

-   State when and how it was originally collected (by the original data curator, not necessarily how you found the data).

-   Write a brief description of the observations.

## Research question

-   A well formulated research question. (You may include more than one research question if you want to receive feedback on different ideas for your project. However, one per data set is required.)
-   A description of the research topic along with a concise statement of your hypotheses on this topic.
-   Identify the types of variables in your research question. Categorical? Quantitative?

## Glimpse of data

```{r}
#| label: load-datasci-salary-dataset

ds_salary <- read.csv("data/ds_salaries.csv") 

glimpse(ds_salary)

```
